\subsection{Classification of runtime}
We can try to classify all these runtime by functionality, we can consider three form of parallelism expression : loop parallelism, PTG and insert task paradigm.
%
The first table~\ref{tab:runtime_family} summarizes capabilities of a set of runtime, a {\it ++} entry means that the capacity is often put forward in publication, a single {\it +} means that the runtime has the functionality but it is not a major advantage of the runtime.
%
The second table~\ref{tab:runtime_archi} summarizes target architecture of the same set of runtime.
%
In the case of distributed memory, we can see two method to address this problem.
An implicit method when the runtime has a memory manager and can do automatic transfer.
Or an explicit method often describe as user task, some runtime, like StarPU, support asynchronous transfer, without this support the explicit method is less efficient.


We can also try to differentiate other differences, like the use of an API ({\it Application Programming Interface}) or the use of a source-to-source compiler.
%
Data management is also important in a runtime to optimize data transfer between CPU and GPU, or between two CPUs.

\begin{table}[h!]
\centering
\begin{tabular}{c|ccc}
  \textit{runtime}& loop parallelism & PTG & Insert task\\
  \hline
        Cilk           &    &    & ++ \\
        Cilk++         & ++ &    & ++ \\
        OpenMP $<$ 3.0 & ++ &    &    \\
        OpenMP 3.x     & ++ &    & +  \\
        OpenMP 4.0     & ++ &    & +  \\
        OpenACC        & ++ &    & +  \\
        Intel TBB      & +  &    & ++ \\
        OMPSs          & +  &    & ++ \\
        Intel CnC      & +  & ++ &    \\
        PaRSEC         &    & ++ &    \\
 PGAS(coarray fortran) & ++ &    &    \\
        StarPU         &    &    & ++ \\
        KAAPI          & ++ &    &    \\
        X-KAAPI        & +  &    & ++
\end{tabular}
\caption{Classification of runtime by capabilities}
\label{tab:runtime_family}
\end{table}

\begin{table}[h!]
\centering
\begin{tabular}{c|ccc}
  \textit{runtime} & Shared memory & Distributed memory & GPU accelerator \\
\hline
        Cilk           & X &           &   \\
        Cilk++         & X &           &   \\
        OpenMP $<$ 3.0 & X &           &   \\
        OpenMP 3.x     & X &           &   \\
        OpenMP 4.0     & X &           & X \\
        OpenACC        & X &           & X \\
        Intel TBB      & X &           &   \\
        OMPSs          & X & explicit  & X \\
        Intel CnC      & X & implicit  &   \\
        PaRSEC         & X & implicit  &   \\
 PGAS(coarray fortran) & X & implicit  &   \\
        StarPU         & X & implicit/explicit  & X \\
        KAAPI          & X &           & X \\
        X-KAAPI        & X & explicit  & X
\end{tabular}
\caption{Classification of runtime by supported architecture}
\label{tab:runtime_archi}
\end{table}
